### 2014-05-15 brains-protocol.tex
Cut substitution figure in two, rename section 3.3

\subsection{Detection of substitutions}

@@

Let us give an example: say the quotation ``These accusations are false and \textbf{absurd}'' ($q_a$) appears in a blog on January 19, and the slightly different quotation ``These accusations are false and \textbf{incoherent}'' ($q_b$) appears in other blogs on the 21st, 22nd and 23rd of January.
If $q_a$ was sufficiently prominent when $q_b$ first appeared, we can safely assume that the first author of $q_b$ on the 21st based himself on $q_a$ as is shown in the top drawing of Figure~\ref{fig:substitution-detection-example1}.
But what about the second and third occurrences of $q_b$, on the 22nd and 23rd?
Should we consider them to be substitutions based on $q_a$ %(i.e. re-creations of $q_b$ by a new instance of the substitution process that brought from $q_a$ to $q_b$ in the first place) 
or accurate reproductions of the previous occurrences of $q_b$? \cam{là je distinguerais 3a [top] de 3b [middle \& bottom]} (options shown in Figure~\ref{fig:substitution-detection-example1})?

\begin{figure}[h]
    \centering
    \def\svgwidth{\linewidth}
    \small
    \input{images/substitution-detection-example1.pdf_tex}
    \caption{XXXXX}
    \label{fig:substitution-detection-example1}
\end{figure}

@@

This model has two main effects.
First, the binning influences how many times quote occurrences can be counted as substitutions: in the second drawing on Figure~\ref{fig:substitution-detection-example1}, occurrences of $q_b$ on the 21st and 22nd are counted as substitutions, whereas the occurrence on the 23rd is not.
Second, the ``majority'' rule defines how quotes are sourced in substitutions: in the third drawing on Figure~\ref{fig:substitution-detection-example1}, $q_b$ holds the majority and is the considered the basis for the last occurrence of $q_a$, in spite of $q_a$ having appeared earlier at the very beginning (indeed in the situation shown in Figure~\ref{fig:substitution-detection-example1}, this seems the most likely scenario).

@@

>>>>

\subsection{Temporal binning}

@@

Let us give an example: say the quotation ``These accusations are false and \textbf{absurd}'' ($q_a$) appears in a blog on January 19, and the slightly different quotation ``These accusations are false and \textbf{incoherent}'' ($q_b$) appears in other blogs on the 21st, 22nd and 23rd of January.
If $q_a$ was sufficiently prominent when $q_b$ first appeared, we can safely assume that the first author of $q_b$ on the 21st based himself on $q_a$ as is shown in the top drawing of Figure~\ref{fig:substitution-detection-example1}.
But what about the second and third occurrences of $q_b$, on the 22nd and 23rd?
Should we consider them to be substitutions based on $q_a$ %(i.e. re-creations of $q_b$ by a new instance of the substitution process that brought from $q_a$ to $q_b$ in the first place) 
or accurate reproductions of the previous occurrences of $q_b$? \cam{là je distinguerais 3a [top] de 3b [middle \& bottom]} (options shown in Figure~\ref{fig:substitution-temporal-binning})?

\begin{figure}[h]
    \centering
    \def\svgwidth{\linewidth}
    \small
    \input{images/substitution-temporal-binning.pdf_tex}
    \caption{XXXXX}
    \label{fig:substitution-temporal-binning}
\end{figure}

@@

This model has two main effects.
First, the binning influences how many times quote occurrences can be counted as substitutions: in the second drawing on Figure~\ref{fig:substitution-temporal-binning}, occurrences of $q_b$ on the 21st and 22nd are counted as substitutions, whereas the occurrence on the 23rd is not.
Second, the ``majority'' rule defines how quotes are sourced in substitutions: in the third drawing on Figure~\ref{fig:substitution-temporal-binning}, $q_b$ holds the majority and is the considered the basis for the last occurrence of $q_a$, in spite of $q_a$ having appeared earlier at the very beginning (indeed in the situation shown in Figure~\ref{fig:substitution-temporal-binning}, this seems the most likely scenario).

@@

\begin{figure}[h]
    \centering
    \def\svgwidth{\linewidth}
    \small
    \input{images/substitution-q_max.pdf_tex}
    \caption{XXXXX}
    \label{fig:substitution-q_max}
\end{figure}
